---
title: "EndPoints CTL08: Target Gene Signatures"
date: 'Date: `r format(Sys.Date(), "%B %d, %Y")`'
output:
    html_document:
        toc: true
        toc_float: true
        theme: 'united'
        highlight: 'kate'
        code_folding: hide
params: 
    Dataset: 'CTL08'
    SE: '~/DataDir/bulkRNASeq/3.DataExploration/CTL08/Output/AfterSamplesSelection/MaleLineSE_Bio.rds'
    OutputFolder: '~/DataDir/bulkRNASeq/4.GeneSignatures/CTL08/Output/AfterSamplesSelection/TargetSig/'
    CpmFilt: 2
    SampleFilt: 4

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```

### Checking gene signatures on `r params$Dataset`

## 1. Environment Set Up
Values of RMarkdown parameters
```{r EnvironmentSetupI, collapse=TRUE}
for (i in 1:length(params))
  print(paste('Parameter:', names(params)[i], ' - Value:', params[[i]], '- Class:', class(params[[i]])))
```

 
```{r EnvironmentSetupII, collapse=TRUE}
library(RNASeqBulkExploratory)  #Our Package
library(DT)
library(gridExtra)
library(SummarizedExperiment)
library(SEtools)
library(sechm)
library(randomcoloR)
library(ggplot2)
library(tidyHeatmap)
```

```{r FolderSetting}
Dataset <- params$Dataset
OutputFolder <- params$OutputFolder

if (dir.exists(OutputFolder) == FALSE) {
  dir.create(OutputFolder, recursive=FALSE)
}
```


****

## 2. Data Upload

### 2.1 SE object

SE object created from exploratory analysis. Steps already performed: gene selection according to biotype.


```{r, collapse=TRUE}
SE_Bio <- readRDS(params$SE)
```

SE object containing information about `r dim(SE_Bio)[1]` genes in `r dim(SE_Bio)[2]` samples. 

```{r}
if(! identical(names(assays(SE_Bio)$counts), rownames(colData(SE_Bio)))){
  stop('Inconsistencies in sample metadata for SE object')
  }

if(! identical(names(assays(SE_Bio)$counts), colData(SE_Bio)$HRID)){
  stop('Inconsistencies in sample metadata for SE object')
  }

```


### 2.2 Gene Lenght

```{r, collapse=TRUE}
GeneLength <- read.table(file = '~/DataDir/bulkRNASeq/1.GeneLength/Output/GenecodeV35GeneLength.txt', 
                         sep='\t', header=TRUE)
```


```{r, collapse=TRUE}
SelLenght <- dplyr::left_join(as.data.frame(rowData(SE_Bio))[,1:3], GeneLength, by=c('Gene'='Gene'))
```


```{r, collapse=TRUE}
if(identical(SelLenght$Gene, rowData(SE_Bio)$Gene)){
  rowData(SE_Bio)$GeneLength <- SelLenght$Length
  print('Gene Lengh information added to SE')
} else {
    print('Information on gene lenght is not compatible with SE object. Gene Lenght information not added to SE')
  }
```

### 2.3 Gene Signatures


```{r, collapse=TRUE}
GS <- read.table(file = '~/DataDir/bulkRNASeq/4.GeneSignatures/GeneSets/TargetGenes.txt', 
                         sep='\t', header=TRUE)
names(GS)[2] <- 'Population'

table(GS$Population)
```


****

## 3. Selecting and filtering

### 3.1 Sample Selection

Already performed.

### 3.2 Gene Filtering

#### 3.2.1 Setting gene filtering thresholds

```{r FiltThresholds, collapse=TRUE}
CpmFilt <- params$CpmFilt
if(is.numeric(CpmFilt)==FALSE){
  stop('ERROR! Cpm threshold for gene filtering has a non-numeric value')
}

SampleFilt <- ifelse(params$SampleFilt=='Default', dim(SE_Bio)[2]/2, params$SampleFilt)
if(is.numeric(SampleFilt)==FALSE){
  stop('ERROR! Sample threshold for gene filtering has a non-numeric value')
}
```

__Genes having an expression lower than `r CpmFilt` in at least `r SampleFilt` samples are filtered out.__


#### 3.2.2 Filter out low expressed genes

 * Compute temporary cpm (without TMM normalization, not stored in SE)
 * Filter out lowly-expressed genes


```{r SE_Filt, collapse=TRUE}
SE_Bio$lib.size
SE_Filt <- filterSE(SE_Bio, cpmTh=CpmFilt, sampleTh=SampleFilt)
#SE_Filt$lib.size
```


#### 3.2.3 Normalize 

 * Re-calculate library size and calculate TMM
 * Calculate cpm and logcpm (with normalization) and store in SE_Filt
 * Calculate Fpkm and logfpkm

```{r SE_norm, collapse=TRUE}
SE_Filt <- normTmmSE(SE_Filt, useNormFactors=TRUE, priorCount=0.25)  

assays(SE_Filt)$fpkm <- edgeR::rpkm(SE_Filt, normalized.lib.sizes = TRUE, gene.length=rowData(SE_Filt)$GeneLength)
assays(SE_Filt)$logfpkm <- edgeR::rpkm(SE_Filt, normalized.lib.sizes = TRUE, gene.length=rowData(SE_Filt)$GeneLength, 
                                  log=TRUE, prior.count=0.25)
```

__After filtering out lowly-expressed genes, the dataset is structured in `r dim(SE_Filt)[1]` genes measured in `r dim(SE_Filt)[2]` samples.__ 


****


## 4. Heatmaps: pre-processing


### 4.1 Gene name as row names


```{r, collapse=TRUE}
rownames(SE_Filt) <- rowData(SE_Filt)$GeneName
SE_Filt <- SE_Filt[!duplicated(rownames(SE_Filt)), ] 
```

### 4.2 Calculate the fold-change 

Calculate the fold-change compared to the controls (DMSO). This is done on logcpm.

```{r, collapse=TRUE}
DMSO <- as.vector(which(SE_Filt$Condition=='DMSO'))
SE_Filt <- SEtools::log2FC(SE_Filt, fromAssay='logcpm', controls=DMSO, isLog=TRUE, toAssay='log2FC')
```


### 4.3 Define the color annotation 

```{r, collapse=TRUE}
colData(SE_Filt)$Condition <- factor(colData(SE_Filt)$Condition, levels=c("CTL", "DMSO", "AhHyd_Ag", "AhHyd_Inh", "Andr_Ag", "Andr_Inh", "Estr_Ag", "Estr_Inh", "GC_Ag", "GC_Inh", "LivX_Ag", "LivX_Inh", "Ret_Ag", "Ret_Inh", "Thyr_Ag", "Thyr_Inh" ))

metadata(SE_Filt)$anno_colors <- list(Condition = c('DMSO' = 'grey30', 'CTL' = 'azure3', 

                 'AhHyd_Ag'='#F8766D', 'AhHyd_Inh'='#F8766D50',

                 'Andr_Ag'='#fccb17', 'Andr_Inh'='#C49A0050',  

                 "Estr_Ag"= '#53B400', "Estr_Inh"= '#53B40050', 

                 'GC_Ag' = '#00C094', 'GC_Inh' = '#00C09450',

                 'LivX_Ag' = '#00B6EB', 'LivX_Inh' = '#00B6EB50', 

                 'Ret_Ag' = '#A58AFF', 'Ret_Inh' = '#A58AFF50', 

                 'Thyr_Ag' = '#FB61D7', 'Thyr_Inh' = '#FB61D750'

                 )
 , SeqRun = c("20210310" = "orange", "20210724"  = "green4", "20220422" = 
                                          "#66ACB7"))
```

****

## 5. Target genes

### 5.1 Gene signature  {.tabset}

```{r, collapse=TRUE}
Genes <- GS %>% dplyr::pull(GeneName)

Genes[! Genes %in% row.names(SE_Filt)]

rowData(SE_Filt)$Signatures <- NA
rowData(SE_Filt)$UpregulatedBy <- NA
rowData(SE_Filt)$DownregulatedBy <- NA

for (i in which(rowData(SE_Filt)$GeneName %in% Genes)){
  gene <- row.names(SE_Filt)[i]
  rowData(SE_Filt)[i, 'Signatures'] <-GS[GS$GeneName==gene, c("Population")]
  rowData(SE_Filt)[i, 'UpregulatedBy'] <-GS[GS$GeneName==gene, c("UpregulatedBy")]
  rowData(SE_Filt)[i, 'DownregulatedBy'] <-GS[GS$GeneName==gene, c("DownregulatedBy")]
}

metadata(SE_Filt)$anno_colors$Signatures <- c(ARYL_HYDROCARBONS = "#F8766D", ANDROGEN = "#fccb17", ESTROGEN = "#53B400", GLUCOCORTICOIDS = "#00C094", LIVERX = "#00B6EB", RETINOIC_ACID = "#A58AFF", THYROID = "#FB61D7")
metadata(SE_Filt)$anno_colors$UpregulatedBy <- c(Agonist = "#ACDCD7", Inhibitor = "#F38692")
metadata(SE_Filt)$anno_colors$DownregulatedBy <- c(Agonist = "#ACDCD7", Inhibitor = "#F38692")

#color for heatmaps
ScaledCols <- c('darkblue', "purple","white","lightgoldenrod1", 'goldenrod1')
```

__The following genes are not selected as expressed:__ `r paste(Genes[! Genes %in% row.names(SE_Filt)])`. 


#### ANDROGEN signatures

```{r collapse=TRUE}
GenesANDR <- GS[which(GS$Population=="ANDROGEN"), "GeneName"]
```

##### 5.2 Expression levels: logfpkm without scaling

```{r , collapse=TRUE,  fig.width=12, fig.height=5}
break_coord <- assays(SE_Filt[row.names(SE_Filt) %in% GenesANDR, ])$logfpkm %>% quantile(seq(0,1, by=0.1))

ExpCols <- viridisLite::cividis(length(seq(head(break_coord,1), tail(break_coord,1), by=0.2)))
```

```{r , collapse=TRUE, fig.width=15, fig.height=5}
p2 <- sechm::sechm(SE_Filt, features=GenesANDR, assayName="logfpkm", gaps_at = "Condition", gaps_row="Signatures", top_annotation = c("Condition", "SeqRun"), show_rownames = TRUE, left_annotation = c("Signatures", "UpregulatedBy", "DownregulatedBy"), sortRowsOn=NULL, cluster_rows=FALSE, cluster_cols = FALSE,  show_colnames=TRUE, hmcols=ExpCols, breaks=seq(head(break_coord,1), tail(break_coord,1), by=0.2), column_title = "Logfpkm")
# breaks FALSE to avoid a symmetrical scale
p2
```

Saving to PDF files

```{r , collapse=TRUE, include=FALSE}
tidyHeatmap::save_pdf(p2, filename=paste0(OutputFolder, 'LogFpkmANDR_all.pdf'), width=15, height=5)
```

##### 5.3 Expression levels: scaled logfpkm

```{r collapse=TRUE, include=FALSE}
GS_Exp <- assays(SE_Filt[row.names(SE_Filt) %in% GenesANDR, ])$logfpkm

GS_Exp
```

```{r , collapse=TRUE, fig.width=15, fig.height=5}
p2 <- sechm::sechm(SE_Filt, features=GenesANDR, assayName="logfpkm", gaps_at = "Condition", gaps_row="Signatures", top_annotation = c("Condition", "SeqRun"), show_rownames = TRUE, left_annotation = c("Signatures", "UpregulatedBy", "DownregulatedBy"), sortRowsOn=NULL, cluster_rows=FALSE, cluster_cols = FALSE,  show_colnames=TRUE, hmcols=ScaledCols, do.scale=TRUE, breaks=0.8, column_title = "Scaled Logfpkm")
p2
```

Saving to PDF files

```{r , collapse=TRUE, include=FALSE}
tidyHeatmap::save_pdf(p2, filename=paste0(OutputFolder, 'ScaledLogfpkmANDR_all.pdf'), width=15, height=5)
```

```{r , collapse=TRUE, fig.width=12, fig.height=5}
p1 <- sechm::sechm(SE_Filt[, grepl('DMSO|Andr', colnames(SE_Filt))], features=GenesANDR, assayName="logfpkm", cluster_cols = TRUE,
             gaps_at = "Condition", gaps_row="Signatures", top_annotation = c("Condition", "SeqRun"), show_rownames = TRUE,
             left_annotation = c("Signatures", "UpregulatedBy", "DownregulatedBy"), sortRowsOn=NULL, cluster_rows=FALSE,
             show_colnames=TRUE,
             hmcols=ScaledCols, do.scale=TRUE, breaks=0.85, column_title = "Scaled Logfpkm with
             clustering")
```

```{r , collapse=TRUE, fig.width=15, fig.height=5}
p2<- sechm::sechm(SE_Filt, features=GenesANDR, assayName="logfpkm", cluster_cols = TRUE,
            gaps_at = "Condition", gaps_row="Signatures", top_annotation = c("Condition", "SeqRun"), show_rownames = TRUE,
            left_annotation = c("Signatures", "UpregulatedBy", "DownregulatedBy"), sortRowsOn=NULL, cluster_rows=FALSE,
             show_colnames=TRUE,
             hmcols=ScaledCols, do.scale=TRUE, breaks=0.85, column_title = "Scaled Logfpkm with
             clustering")
```


##### 5.4 Expression levels: Log2FC versus DMSO

```{r ,    collapse=TRUE,  fig.width=15, fig.height=5}
p2 <- sechm::sechm(SE_Filt, features=GenesANDR, assayName="log2FC", gaps_at = "Condition", gaps_row="Signatures", top_annotation = c("Condition", "SeqRun"), show_rownames = TRUE, left_annotation = c("Signatures", "UpregulatedBy", "DownregulatedBy"), sortRowsOn=NULL, cluster_rows=FALSE, cluster_cols = FALSE,  show_colnames=TRUE, hmcols=ScaledCols, 
      do.scale=FALSE, breaks = 0.85, column_title = "LogFC versus DMSO")
p2
```

Saving to PDF files

```{r , collapse=TRUE, include=FALSE}
tidyHeatmap::save_pdf(p2, filename=paste0(OutputFolder, 'LogFCANDR_all.pdf'), width=15, height=5)
```

#### THYROID signatures

```{r collapse=TRUE}
GenesTHYR<- GS[which(GS$Population=="THYROID"), "GeneName"]
```

##### 5.2 Expression levels: logFpkm without scaling

```{r , collapse=TRUE,  fig.width=12, fig.height=5}
break_coord <- assays(SE_Filt[row.names(SE_Filt) %in% GenesTHYR, ])$logfpkm %>% quantile(seq(0,1, by=0.1))

ExpCols <- viridisLite::cividis(length(seq(head(break_coord,1), tail(break_coord,1), by=0.2)))
```

```{r , collapse=TRUE,  fig.width=15, fig.height=5}
p2 <- sechm::sechm(SE_Filt, features=GenesTHYR, assayName="logfpkm", gaps_at = "Condition", gaps_row="Signatures", top_annotation = c("Condition", "SeqRun"), show_rownames = TRUE, left_annotation = c("Signatures", "UpregulatedBy", "DownregulatedBy"), sortRowsOn=NULL, cluster_rows=FALSE, cluster_cols = FALSE,  show_colnames=TRUE, hmcols=ExpCols, breaks=seq(head(break_coord,1), tail(break_coord,1), by=0.2), column_title = "LogFpkm")
# breaks FALSE to avoid a symmetrical scale
p2
```

Saving to PDF files

```{r , collapse=TRUE, include=FALSE}
tidyHeatmap::save_pdf(p2, filename=paste0(OutputFolder, 'LogFpkmTHYR_all.pdf'), width=15, height=5)
```

##### 5.3 Expression levels: scaled logfpkm

```{r collapse=TRUE, include=FALSE}
GS_Exp <- assays(SE_Filt[row.names(SE_Filt) %in% GenesTHYR, ])$logfpkm

GS_Exp
```



```{r , collapse=TRUE, fig.width=15, fig.height=5}
p2 <- sechm::sechm(SE_Filt, features=GenesTHYR, assayName="logfpkm", gaps_at = "Condition", gaps_row="Signatures", top_annotation = c("Condition", "SeqRun"), show_rownames = TRUE, left_annotation = c("Signatures", "UpregulatedBy", "DownregulatedBy"), sortRowsOn=NULL, cluster_rows=FALSE, cluster_cols = FALSE,  show_colnames=TRUE, hmcols=ScaledCols, do.scale=TRUE, breaks=0.8, column_title = "Scaled Logfpkm")
p2
```

Saving to PDF files

```{r , collapse=TRUE, include=FALSE}
tidyHeatmap::save_pdf(p2, filename=paste0(OutputFolder, 'ScaledLogfpkmTHYR_all.pdf'), width=15, height=5)
```


```{r , collapse=TRUE, fig.width=15, fig.height=10}
p2 <- sechm::sechm(SE_Filt, features=GenesTHYR, assayName="logfpkm", cluster_cols = TRUE,
             gaps_row="Signatures", top_annotation = c("Pathway", "Condition", "SeqRun"), show_rownames = TRUE,
             left_annotation = c("Signatures", "UpregulatedBy", "DownregulatedBy"), sortRowsOn=NULL, cluster_rows=FALSE,
             show_colnames=TRUE,
             hmcols=ScaledCols, do.scale=TRUE, breaks=0.85, column_title = "Scaled Logfpkm with
             clustering")
```


##### 5.4 Expression levels: Log2FC versus DMSO


```{r ,    collapse=TRUE,  fig.width=15, fig.height=5}
p2 <- sechm::sechm(SE_Filt, features=GenesTHYR, assayName="log2FC", gaps_at = "Condition", gaps_row="Signatures", top_annotation = c("Condition", "SeqRun"), show_rownames = TRUE, left_annotation = c("Signatures", "UpregulatedBy", "DownregulatedBy"), sortRowsOn=NULL, cluster_rows=FALSE, cluster_cols = FALSE,  show_colnames=TRUE, hmcols=ScaledCols, 
      do.scale=FALSE, breaks = 0.85, column_title = "LogFC versus DMSO")
p2
```

Saving to PDF files


```{r , collapse=TRUE, include=FALSE}
tidyHeatmap::save_pdf(p2, filename=paste0(OutputFolder, 'LogFCTHYR_all.pdf'), width=15, height=5)
```

#### ESTROGEN signatures

```{r collapse=TRUE}
GenesESTR<- GS[which(GS$Population=="ESTROGEN"), "GeneName"]
```

##### 5.2 Expression levels: logFpkm without scaling

```{r , collapse=TRUE,  fig.width=12, fig.height=5}
break_coord <- assays(SE_Filt[row.names(SE_Filt) %in% GenesESTR, ])$logfpkm %>% quantile(seq(0,1, by=0.1))

ExpCols <- viridisLite::cividis(length(seq(head(break_coord,1), tail(break_coord,1), by=0.2)))
```

```{r , collapse=TRUE,  fig.width=15, fig.height=5}
p2 <- sechm::sechm(SE_Filt, features=GenesESTR, assayName="logfpkm", gaps_at = "Condition", gaps_row="Signatures", top_annotation = c("Condition", "SeqRun"), show_rownames = TRUE, left_annotation = c("Signatures", "UpregulatedBy", "DownregulatedBy"), sortRowsOn=NULL, cluster_rows=FALSE, cluster_cols = FALSE,  show_colnames=TRUE, hmcols=ExpCols, breaks=seq(head(break_coord,1), tail(break_coord,1), by=0.2), column_title = "LogFpkm")
# breaks FALSE to avoid a symmetrical scale
p2
```

Saving to PDF files


```{r , collapse=TRUE, include=FALSE}
tidyHeatmap::save_pdf(p2, filename=paste0(OutputFolder, 'LogFpkmESTR_all.pdf'), width=15, height=5)
```

##### 5.3 Expression levels: scaled logfpkm

```{r collapse=TRUE, include=FALSE}
GS_Exp <- assays(SE_Filt[row.names(SE_Filt) %in% GenesESTR, ])$logfpkm

GS_Exp
```


```{r , collapse=TRUE, fig.width=15, fig.height=5}
p2 <- sechm::sechm(SE_Filt, features=GenesESTR, assayName="logfpkm", gaps_at = "Condition", gaps_row="Signatures", top_annotation = c("Condition", "SeqRun"), show_rownames = TRUE, left_annotation = c("Signatures", "UpregulatedBy", "DownregulatedBy"), sortRowsOn=NULL, cluster_rows=FALSE, cluster_cols = FALSE,  show_colnames=TRUE, hmcols=ScaledCols, do.scale=TRUE, breaks=0.8, column_title = "Scaled Logfpkm")
p2
``` 

Saving to PDF files


```{r , collapse=TRUE, include=FALSE}
tidyHeatmap::save_pdf(p2, filename=paste0(OutputFolder, 'ScaledLogfpkmESTR_all.pdf'), width=15, height=5)
```

```{r , collapse=TRUE, fig.width=12, fig.height=5}
p1 <- sechm::sechm(SE_Filt[, grepl('DMSO|Estr', colnames(SE_Filt))], features=GenesESTR, assayName="logfpkm", cluster_cols=TRUE,
             gaps_row="Signatures", top_annotation = c("Pathway", "Condition", "SeqRun"), show_rownames = TRUE,
             left_annotation = c("Signatures", "UpregulatedBy", "DownregulatedBy"), sortRowsOn=NULL, cluster_rows=FALSE,
             show_colnames=TRUE,
             hmcols=ScaledCols, do.scale=TRUE, breaks=0.85, column_title = "Scaled Logfpkm with
             clustering")
#p1
```

```{r , collapse=TRUE, fig.width=15, fig.height=10}
p2 <- sechm::sechm(SE_Filt, features=GenesESTR, assayName="logfpkm", cluster_cols=TRUE,
             gaps_row="Signatures", top_annotation = c("Pathway", "Condition", "SeqRun"), show_rownames = TRUE,
             left_annotation = c("Signatures", "UpregulatedBy", "DownregulatedBy"), sortRowsOn=NULL, cluster_rows=FALSE,
             show_colnames=TRUE,
             hmcols=ScaledCols, do.scale=TRUE, breaks=0.85, column_title = "Scaled Logfpkm with
             clustering")
#p2
```


##### 5.4 Expression levels: Log2FC versus DMSO


```{r ,    collapse=TRUE,  fig.width=15, fig.height=5}
p2 <- sechm::sechm(SE_Filt, features=GenesESTR, assayName="log2FC", gaps_at = "Condition", gaps_row="Signatures", top_annotation = c("Condition", "SeqRun"), show_rownames = TRUE, left_annotation = c("Signatures", "UpregulatedBy", "DownregulatedBy"), sortRowsOn=NULL, cluster_rows=FALSE, cluster_cols = FALSE,  show_colnames=TRUE, hmcols=ScaledCols, 
      do.scale=FALSE, breaks = 0.85, column_title = "LogFC versus DMSO")
p2
```

Saving to PDF files

```{r , collapse=TRUE, include=FALSE}
tidyHeatmap::save_pdf(p2, filename=paste0(OutputFolder, 'LogFCESTR_all.pdf'), width=15, height=5)
```

#### LIVER-X signatures

```{r collapse=TRUE}
GenesLIVX<- GS[which(GS$Population=="LIVERX"), "GeneName"]
```

##### 5.2 Expression levels: logFpkm without scaling

```{r , collapse=TRUE,  fig.width=12, fig.height=5}
break_coord <- assays(SE_Filt[row.names(SE_Filt) %in% GenesLIVX, ])$logfpkm %>% quantile(seq(0,1, by=0.1))

ExpCols <- viridisLite::cividis(length(seq(head(break_coord,1), tail(break_coord,1), by=0.2)))
```

```{r , collapse=TRUE,  fig.width=15, fig.height=5}
p2 <- sechm::sechm(SE_Filt, features=GenesLIVX, assayName="logfpkm", gaps_at = "Condition", gaps_row="Signatures", top_annotation = c("Condition", "SeqRun"), show_rownames = TRUE, left_annotation = c("Signatures", "UpregulatedBy", "DownregulatedBy"), sortRowsOn=NULL, cluster_rows=FALSE, cluster_cols = FALSE,  show_colnames=TRUE, hmcols=ExpCols, breaks=seq(head(break_coord,1), tail(break_coord,1), by=0.2), column_title = "LogFpkm")
# breaks FALSE to avoid a symmetrical scale
p2
```

Saving to PDF files


```{r , collapse=TRUE, include=FALSE}
tidyHeatmap::save_pdf(p2, filename=paste0(OutputFolder, 'LogFpkmLIVX_all.pdf'), width=15, height=5)
```

##### 5.3 Expression levels: scaled logfpkm

```{r collapse=TRUE, include=FALSE}
GS_Exp <- assays(SE_Filt[row.names(SE_Filt) %in% GenesLIVX, ])$logfpkm

GS_Exp
```


```{r , collapse=TRUE, fig.width=15, fig.height=5}
p2 <- sechm::sechm(SE_Filt, features=GenesLIVX, assayName="logfpkm", gaps_at = "Condition", gaps_row="Signatures", top_annotation = c("Condition", "SeqRun"), show_rownames = TRUE, left_annotation = c("Signatures", "UpregulatedBy", "DownregulatedBy"), sortRowsOn=NULL, cluster_rows=FALSE, cluster_cols = FALSE,  show_colnames=TRUE, hmcols=ScaledCols, do.scale=TRUE, breaks=0.8, column_title = "Scaled Logfpkm")
p2
```

Saving to PDF files


```{r , collapse=TRUE, include=FALSE}
tidyHeatmap::save_pdf(p2, filename=paste0(OutputFolder, 'ScaledLogfpkmLIVX_all.pdf'), width=15, height=5)
```

```{r , collapse=TRUE, fig.width=12, fig.height=5}
p1 <- sechm::sechm(SE_Filt[, grepl('DMSO|LivX', colnames(SE_Filt))], features=GenesLIVX, assayName="logfpkm", cluster_cols=TRUE,
            gaps_at = "Condition", gaps_row="Signatures", top_annotation = c("Condition", "SeqRun"), show_rownames = TRUE, left_annotation = c("Signatures", "UpregulatedBy", "DownregulatedBy"), sortRowsOn=NULL, cluster_rows=FALSE,
             show_colnames=TRUE,
             hmcols=ScaledCols, do.scale=TRUE, breaks=0.85, column_title = "Scaled Logfpkm with
             clustering")
#p1
```

```{r , collapse=TRUE, fig.width=15, fig.height=10}
p2 <- sechm::sechm(SE_Filt, features=GenesLIVX, assayName="logfpkm", cluster_cols=TRUE,
             gaps_at = "Condition", gaps_row="Signatures", top_annotation = c("Condition", "SeqRun"), show_rownames = TRUE, left_annotation = c("Signatures", "UpregulatedBy", "DownregulatedBy"), sortRowsOn=NULL, cluster_rows=FALSE,
             show_colnames=TRUE,
             hmcols=ScaledCols, do.scale=TRUE, breaks=0.85, column_title = "Scaled Logfpkm with
             clustering")
#p2
```


##### 5.4 Expression levels: Log2FC versus DMSO


```{r ,    collapse=TRUE,  fig.width=15, fig.height=5}
p2 <- sechm::sechm(SE_Filt, features=GenesLIVX, assayName="log2FC", gaps_at = "Condition", gaps_row="Signatures", top_annotation = c("Condition", "SeqRun"), show_rownames = TRUE, left_annotation = c("Signatures", "UpregulatedBy", "DownregulatedBy"), sortRowsOn=NULL, cluster_rows=FALSE, cluster_cols = FALSE,  show_colnames=TRUE, hmcols=ScaledCols, 
      do.scale=FALSE, breaks = 0.85, column_title = "LogFC versus DMSO")
p2
```

Saving to PDF files


```{r , collapse=TRUE, include=FALSE}
tidyHeatmap::save_pdf(p2, filename=paste0(OutputFolder, 'LOGFCLIVX_all.pdf'), width=15, height=5)
```

#### RETINOIC ACID signatures

```{r collapse=TRUE}
GenesRet<- GS[which(GS$Population=="RETINOIC_ACID"), "GeneName"]
```

##### 5.2 Expression levels: logFpkm without scaling

```{r , collapse=TRUE,  fig.width=12, fig.height=5}
break_coord <- assays(SE_Filt[row.names(SE_Filt) %in% GenesRet, ])$logfpkm %>% quantile(seq(0,1, by=0.1))

ExpCols <- viridisLite::cividis(length(seq(head(break_coord,1), tail(break_coord,1), by=0.2)))
```

```{r , collapse=TRUE,  fig.width=15, fig.height=5}
p2 <- sechm::sechm(SE_Filt, features=GenesRet, assayName="logfpkm", gaps_at = "Condition", gaps_row="Signatures", top_annotation = c("Condition", "SeqRun"), show_rownames = TRUE, left_annotation = c("Signatures", "UpregulatedBy", "DownregulatedBy"), sortRowsOn=NULL, cluster_rows=FALSE, cluster_cols = FALSE,  show_colnames=TRUE, hmcols=ExpCols, breaks=seq(head(break_coord,1), tail(break_coord,1), by=0.2), column_title = "LogFpkm")
# breaks FALSE to avoid a symmetrical scale
p2
```

Saving to PDF files

```{r , collapse=TRUE, include=FALSE}
tidyHeatmap::save_pdf(p2, filename=paste0(OutputFolder, 'LogFpkmRET_all.pdf'), width=15, height=5)
```

##### 5.3 Expression levels: scaled logfpkm

```{r collapse=TRUE, include=FALSE}
GS_Exp <- assays(SE_Filt[row.names(SE_Filt) %in% GenesRet, ])$logfpkm

GS_Exp
```


```{r , collapse=TRUE, fig.width=15, fig.height=5}
p2 <- sechm::sechm(SE_Filt, features=GenesRet, assayName="logfpkm", gaps_at = "Condition", gaps_row="Signatures", top_annotation = c("Condition", "SeqRun"), show_rownames = TRUE, left_annotation = c("Signatures", "UpregulatedBy", "DownregulatedBy"), sortRowsOn=NULL, cluster_rows=FALSE, cluster_cols = FALSE,  show_colnames=TRUE, hmcols=ScaledCols, do.scale=TRUE, breaks=0.8, column_title = "Scaled Logfpkm")
p2
```

Saving to PDF files


```{r , collapse=TRUE, include=FALSE}
tidyHeatmap::save_pdf(p2, filename=paste0(OutputFolder, 'ScaledLogfpkmRET_all.pdf'), width=15, height=5)
```

```{r , collapse=TRUE, fig.width=12, fig.height=5}
p1 <- sechm::sechm(SE_Filt[, grepl('DMSO|Ret', colnames(SE_Filt))], features=GenesRet, assayName="logfpkm", cluster_cols=TRUE,
             gaps_at = "Condition", gaps_row="Signatures", top_annotation = c("Condition", "SeqRun"), show_rownames = TRUE, left_annotation = c("Signatures", "UpregulatedBy", "DownregulatedBy"), sortRowsOn=NULL, cluster_rows=FALSE,
             show_colnames=TRUE,
             hmcols=ScaledCols, do.scale=TRUE, breaks=0.85, column_title = "Scaled Logfpkm with
             clustering")
#p1
```

```{r , collapse=TRUE, fig.width=15, fig.height=10}
p2 <- sechm::sechm(SE_Filt, features=GenesRet, assayName="logfpkm", cluster_cols=TRUE,
             gaps_at = "Condition", gaps_row="Signatures", top_annotation = c("Condition", "SeqRun"), show_rownames = TRUE, left_annotation = c("Signatures", "UpregulatedBy", "DownregulatedBy"), sortRowsOn=NULL, cluster_rows=FALSE,
             show_colnames=TRUE,
             hmcols=ScaledCols, do.scale=TRUE, breaks=0.85, column_title = "Scaled Logfpkm with
             clustering")
#p2
```


##### 5.4 Expression levels: Log2FC versus DMSO

```{r ,    collapse=TRUE,  fig.width=15, fig.height=5}
p2 <- sechm::sechm(SE_Filt, features=GenesRet, assayName="log2FC", gaps_at = "Condition", gaps_row="Signatures", top_annotation = c("Condition", "SeqRun"), show_rownames = TRUE, left_annotation = c("Signatures", "UpregulatedBy", "DownregulatedBy"), sortRowsOn=NULL, cluster_rows=FALSE, cluster_cols = FALSE,  show_colnames=TRUE, hmcols=ScaledCols, 
      do.scale=FALSE, breaks = 0.85, column_title = "LogFC versus DMSO")
p2
```

Saving to PDF files


```{r , collapse=TRUE, include=FALSE}
tidyHeatmap::save_pdf(p2, filename=paste0(OutputFolder, 'LogFCRET_all.pdf'), width=15, height=5)
```

#### ARYL HYDROCARBONS signatures

```{r collapse=TRUE}
GenesAhHyd<- GS[which(GS$Population=="ARYL_HYDROCARBONS"), "GeneName"]
```

##### 5.2 Expression levels: logFpkm without scaling

```{r , collapse=TRUE,  fig.width=12, fig.height=5}
break_coord <- assays(SE_Filt[row.names(SE_Filt) %in% GenesAhHyd, ])$logfpkm %>% quantile(seq(0,1, by=0.1))

ExpCols <- viridisLite::cividis(length(seq(head(break_coord,1), tail(break_coord,1), by=0.2)))
```

```{r , collapse=TRUE,  fig.width=15, fig.height=5}
p2 <- sechm::sechm(SE_Filt, features=GenesAhHyd, assayName="logfpkm", gaps_at = "Condition", gaps_row="Signatures", top_annotation = c("Condition", "SeqRun"), show_rownames = TRUE, left_annotation = c("Signatures", "UpregulatedBy", "DownregulatedBy"), sortRowsOn=NULL, cluster_rows=FALSE, cluster_cols = FALSE,  show_colnames=TRUE, hmcols=ExpCols, breaks=seq(head(break_coord,1), tail(break_coord,1), by=0.2), column_title = "LogFpkm")
# breaks FALSE to avoid a symmetrical scale
p2
```

Saving to PDF files

```{r , collapse=TRUE, include=FALSE}
tidyHeatmap::save_pdf(p2, filename=paste0(OutputFolder, 'LogFpkmAhhyd_all.pdf'), width=15, height=5)
```

##### 5.3 Expression levels: scaled logfpkm

```{r collapse=TRUE, include=FALSE}
GS_Exp <- assays(SE_Filt[row.names(SE_Filt) %in% GenesAhHyd, ])$logfpkm

GS_Exp
```


```{r , collapse=TRUE, fig.width=15, fig.height=5}
p2 <- sechm::sechm(SE_Filt, features=GenesAhHyd, assayName="logfpkm", gaps_at = "Condition", gaps_row="Signatures", top_annotation = c("Condition", "SeqRun"), show_rownames = TRUE, left_annotation = c("Signatures", "UpregulatedBy", "DownregulatedBy"), sortRowsOn=NULL, cluster_rows=FALSE, cluster_cols = FALSE,  show_colnames=TRUE, hmcols=ScaledCols, do.scale=TRUE, breaks=0.8, column_title = "Scaled Logfpkm")
p2
```

Saving to PDF files


```{r , collapse=TRUE, include=FALSE}
tidyHeatmap::save_pdf(p2, filename=paste0(OutputFolder, 'ScaledLogfpkmAhHyd_all.pdf'), width=15, height=5)
```

```{r , collapse=TRUE, fig.width=12, fig.height=5}
p1 <- sechm::sechm(SE_Filt[, grepl('DMSO|AhHyd', colnames(SE_Filt))], features=GenesAhHyd, assayName="logfpkm", cluster_cols=TRUE,
             gaps_at = "Condition", gaps_row="Signatures", top_annotation = c("Condition", "SeqRun"), show_rownames = TRUE, left_annotation = c("Signatures", "UpregulatedBy", "DownregulatedBy"), sortRowsOn=NULL, cluster_rows=FALSE,
             show_colnames=TRUE,
             hmcols=ScaledCols, do.scale=TRUE, breaks=0.85, column_title = "Scaled Logfpkm with
             clustering")
#p1
```

```{r , collapse=TRUE, fig.width=15, fig.height=10}
p2 <- sechm::sechm(SE_Filt, features=GenesAhHyd, assayName="logfpkm", cluster_cols=TRUE,
             gaps_at = "Condition", gaps_row="Signatures", top_annotation = c("Condition", "SeqRun"), show_rownames = TRUE, left_annotation = c("Signatures", "UpregulatedBy", "DownregulatedBy"), sortRowsOn=NULL, cluster_rows=FALSE,
             show_colnames=TRUE,
             hmcols=ScaledCols, do.scale=TRUE, breaks=0.85, column_title = "Scaled Logfpkm with
             clustering")
#p2
```



##### 5.4 Expression levels: Log2FC versus DMSO


```{r ,    collapse=TRUE,  fig.width=15, fig.height=5}
p2 <- sechm::sechm(SE_Filt, features=GenesAhHyd, assayName="log2FC", gaps_at = "Condition", gaps_row="Signatures", top_annotation = c("Condition", "SeqRun"), show_rownames = TRUE, left_annotation = c("Signatures", "UpregulatedBy", "DownregulatedBy"), sortRowsOn=NULL, cluster_rows=FALSE, cluster_cols = FALSE,  show_colnames=TRUE, hmcols=ScaledCols, 
      do.scale=FALSE, breaks = 0.85, column_title = "LogFC versus DMSO")
p2
```

Saving to PDF files


```{r , collapse=TRUE, include=FALSE}
tidyHeatmap::save_pdf(p2, filename=paste0(OutputFolder, 'LogFCAhHyd_all.pdf'), width=15, height=5)
```

#### GLUCOCORTICOIDS signatures

```{r collapse=TRUE}
GenesGC<- GS[which(GS$Population=="GLUCOCORTICOIDS"), "GeneName"]
```

##### 5.2 Expression levels: logFpkm without scaling

```{r , collapse=TRUE,  fig.width=12, fig.height=5}
break_coord <- assays(SE_Filt[row.names(SE_Filt) %in% GenesGC, ])$logfpkm %>% quantile(seq(0,1, by=0.1))

ExpCols <- viridisLite::cividis(length(seq(head(break_coord,1), tail(break_coord,1), by=0.2)))
```

```{r , collapse=TRUE,  fig.width=15, fig.height=5}
p2 <- sechm::sechm(SE_Filt, features=GenesGC, assayName="logfpkm", gaps_at = "Condition", gaps_row="Signatures", top_annotation = c("Condition", "SeqRun"), show_rownames = TRUE, left_annotation = c("Signatures", "UpregulatedBy", "DownregulatedBy"), sortRowsOn=NULL, cluster_rows=FALSE, cluster_cols = FALSE,  show_colnames=TRUE, hmcols=ExpCols, breaks=seq(head(break_coord,1), tail(break_coord,1), by=0.2), column_title = "LogFpkm")
# breaks FALSE to avoid a symmetrical scale
p2
```

Saving to PDF files

```{r , collapse=TRUE, include=FALSE}
tidyHeatmap::save_pdf(p2, filename=paste0(OutputFolder, 'LogFpkmGC_all.pdf'), width=15, height=5)
```

##### 5.3 Expression levels: scaled logfpkm

```{r collapse=TRUE, include=FALSE}
GS_Exp <- assays(SE_Filt[row.names(SE_Filt) %in% GenesGC, ])$logfpkm

GS_Exp
```

```{r , collapse=TRUE, fig.width=15, fig.height=5}
p2 <- sechm::sechm(SE_Filt, features=GenesGC, assayName="logfpkm", gaps_at = "Condition", gaps_row="Signatures", top_annotation = c("Condition", "SeqRun"), show_rownames = TRUE, left_annotation = c("Signatures", "UpregulatedBy", "DownregulatedBy"), sortRowsOn=NULL, cluster_rows=FALSE, cluster_cols = FALSE,  show_colnames=TRUE, hmcols=ScaledCols, do.scale=TRUE, breaks=0.8, column_title = "Scaled Logfpkm")
p2
```

Saving to PDF files


```{r , collapse=TRUE, include=FALSE}
tidyHeatmap::save_pdf(p2, filename=paste0(OutputFolder, 'ScaledLogfpkmGC_all.pdf'), width=15, height=5)
```


```{r , collapse=TRUE, fig.width=12, fig.height=5}
p1 <- sechm::sechm(SE_Filt[, grepl('DMSO|GC', colnames(SE_Filt))], features=GenesGC, assayName="logfpkm", cluster_cols=TRUE,
             gaps_at = "Condition", gaps_row="Signatures", top_annotation = c("Condition", "SeqRun"), show_rownames = TRUE, left_annotation = c("Signatures", "UpregulatedBy", "DownregulatedBy"), sortRowsOn=NULL, cluster_rows=FALSE,
             show_colnames=TRUE,
             hmcols=ScaledCols, do.scale=TRUE, breaks=0.85, column_title = "Scaled Logfpkm with
             clustering")
#p1
```

```{r , collapse=TRUE, fig.width=15, fig.height=10}
p2 <- sechm::sechm(SE_Filt, features=GenesGC, assayName="logfpkm", cluster_cols=TRUE,
             gaps_at = "Condition", gaps_row="Signatures", top_annotation = c("Condition", "SeqRun"), show_rownames = TRUE, left_annotation = c("Signatures", "UpregulatedBy", "DownregulatedBy"), sortRowsOn=NULL, cluster_rows=FALSE,
             show_colnames=TRUE,
             hmcols=ScaledCols, do.scale=TRUE, breaks=0.85, column_title = "Scaled Logfpkm with
             clustering")
#p2
```


##### 5.4 Expression levels: Log2FC versus DMSO

```{r ,    collapse=TRUE,  fig.width=15, fig.height=5}
p2 <- sechm::sechm(SE_Filt, features=GenesGC, assayName="log2FC", gaps_at = "Condition", gaps_row="Signatures", top_annotation = c("Condition", "SeqRun"), show_rownames = TRUE, left_annotation = c("Signatures", "UpregulatedBy", "DownregulatedBy"), sortRowsOn=NULL, cluster_rows=FALSE, cluster_cols = FALSE,  show_colnames=TRUE, hmcols=ScaledCols, 
      do.scale=FALSE, breaks = 0.85, column_title = "LogFC versus DMSO")
p2
```

Saving to PDF files


```{r , collapse=TRUE, include=FALSE}
tidyHeatmap::save_pdf(p2, filename=paste0(OutputFolder, 'LogFCGC_all.pdf'), width=15, height=5)
```


****

## 6. Savings


```{r SaveSession}
SessionInfo <- sessionInfo()
Date <- date()
save.image(paste0(OutputFolder, '/', Dataset, 'SigTarget_Workspace.RData'))
```

```{r SessionInfo}
Date
SessionInfo
``` 






