---
title: "Bulk RNASeq: additional exploratory plots - CTL08"
date: 'Date: `r format(Sys.Date(), "%B %d, %Y")`'
output:
    html_document:
        toc: true
        toc_float: true
        theme: 'united'
        highlight: 'kate'
        code_folding: hide
params: 
    SEBio: "~/DataDir/bulkRNASeq/3.DataExploration/CTL08/Output/AfterSamplesSelection/MaleLineSE_Bio.rds"
    OutputFolder: '~/'
    CpmFilt: 2
    SampleFilt: 4
---

## Exploratory analysis on `r params$Dataset`

### 1. Environment Set Up

```{r}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
```

```{r EnvironmentSetupII, collapse=TRUE}
library(RNASeqBulkExploratory)  #Our Package
library(DT)
library(gridExtra)
library(SummarizedExperiment)
library(ggplot2)
```

```{r FolderSetting}
SE_Bio <- readRDS(params$SEBio)
CpmFilt <- params$CpmFilt
SampleFilt <- params$SampleFilt
OutputFolder <- params$OutputFolder
```

****

### 2. Data Upload

```{r SE_Filt, collapse=TRUE}
SE_Filt <- filterSE(SE_Bio, cpmTh=CpmFilt, sampleTh=SampleFilt)
```

 * Re-calculate library size and calculate TMM
 * Calculate cpm and logCpm (with normalization) and store in SE_Filt

```{r SE_norm, collapse=TRUE}
SE_Filt <- normTmmSE(SE_Filt, useNormFactors=TRUE, priorCount=0.25)  
```


### 3. Sample-to-sample correlation heatmap

Correlation matrix across samples calculated on the basis of the Spearman correlation. Heatmap annotation takes into consideration sample 'Condition' by default. 

```{r HeatmapSize, collapse=TRUE}
# Set heatmap size on the basis of the number of samples
Width <- 7 + (dim(SE_Filt)[2]- 8) * 0.24
Width <- ifelse(Width<=14, Width, 14)
Height <- 5 + (dim(SE_Filt)[2]- 8) * 0.22
```

```{r PCACol, collapse=TRUE}
Cols <- c('DMSO' = 'grey30', 'CTL' = 'azure3', 
                 'AhHyd_Ag'='#F8766D', 'AhHyd_Inh'='#F8766D50',
                 'Andr_Ag'='#fccb17', 'Andr_Inh'='#C49A0050',  
                 "Estr_Ag"= '#53B400', "Estr_Inh"= '#53B40050', 
                 'GC_Ag' = '#00C094', 'GC_Inh' = '#00C09450',
                 'LivX_Ag' = '#00B6EB', 'LivX_Inh' = '#00B6EB50', 
                 'Ret_Ag' = '#A58AFF', 'Ret_Inh' = '#A58AFF50', 
                 'Thyr_Ag' = '#FB61D7', 'Thyr_Inh' = '#FB61D750'
                 )

colData(SE_Filt)$SeqRun <- factor(colData(SE_Filt)$SeqRun,
                                  levels = c("20210310", "20210724", "20220422"),
                                  labels = c("batch1_run1", "batch1_run2", "batch2_run3"))

seqrun_cols <- c(
  "batch1_run1" = "#0072B2",  
  "batch1_run2" = "#D55E00",  
  "batch2_run3" = "#CC79A7"   
)
```


```{r, fig.align='center', collapse=TRUE}
cond_order <- c("CTL", "DMSO")
other_cond <- setdiff(unique(colData(SE_Filt)$Condition), cond_order)
cond_levels <- c(cond_order, sort(other_cond))
colData(SE_Filt)$Condition <- factor(
  colData(SE_Filt)$Condition,
  levels = cond_levels
)
ord <- order(colData(SE_Filt)$Condition)

SE_Filt_ord <- SE_Filt[, ord]
```


```{r}
sampleCorrHeatmap2 <- function(
    SE,
    plotTitle = NULL,
    annotation_col = NULL,
    annotation_colors = NULL,
    myPalette = NULL,
    display_numbers = TRUE,
    ...
) {
    if (is.null(plotTitle)) {
        plotTitle <- deparse(substitute(SE))
    }

    if (is.null(annotation_col)) {
        ann_fields <- match("Condition", names(colData(SE)))
        if (is.na(ann_fields)) {
            warning("The SE object does not contain the default 'Condition' annotation field")
            ann_fields <- integer(0)
        }
    } else {
        ann_fields <- match(annotation_col, names(colData(SE)))
        if (any(is.na(ann_fields))) {
            warning(
                paste(
                    "WARNING: missing annotation field(s):",
                    paste(annotation_col[is.na(ann_fields)], collapse = ", ")
                )
            )
            ann_fields <- ann_fields[!is.na(ann_fields)]
        }
    }

    annotation_df <- as.data.frame(colData(SE)[ann_fields])

    if (!("logcpm" %in% names(assays(SE)))) {
        stop('SE object has no "logcpm" assay, please use normTmmSE() to compute it')
    }

    SampleCorr <- stats::cor(assays(SE)$logcpm, method = "spearman")

    if (is.null(myPalette)) {
        GreenCols <- grDevices::colorRampPalette(
            RColorBrewer::brewer.pal(7, "Greens")
        )(255)
    } else {
        GreenCols <- myPalette
    }

    if (ncol(SE) > 20) {
        display_numbers <- FALSE
        message('There are many samples. For readability "display_numbers" will be set to FALSE')
    }

    pheatmap::pheatmap(
        as.matrix(SampleCorr),
        main = paste(plotTitle, "\n Spearman correlation"),
        col = GreenCols,
        annotation_col = annotation_df,
        annotation_colors = annotation_colors,
        fontsize_col = 6,
        fontsize_row = 6,
        clustering_method = "average",
        display_numbers = display_numbers,
        ...
    )
}
```

```{r}
sampleCorrHeatmap2(
  SE_Filt_ord,
  plotTitle = "Filtered dataset",
  annotation_col = c("SeqRun", "Condition"),
  annotation_colors = list(
    Condition = Cols,
    SeqRun = seqrun_cols),
  display_numbers = TRUE,
  cluster_rows = TRUE,
  cluster_cols = TRUE,
  show_rownames = FALSE,
  show_colnames = FALSE
)
```

```{r}
ggsave(filename=paste0(OutputFolder, 'PAPER_CORRPLOTS/SampleCorr_CTL08_v2.pdf'), 
       plot=sampleCorrHeatmap2(
  SE_Filt_ord,
  plotTitle = "Filtered dataset",
  annotation_col = c("SeqRun", "Condition"),
  annotation_colors = list(
    Condition = Cols,
    SeqRun = seqrun_cols),
  display_numbers = TRUE,
  cluster_rows = FALSE,
  cluster_cols = FALSE,
  show_rownames = FALSE,
  show_colnames = FALSE
),
       device='pdf', width=5, height=5)
```

### 4. Principal Component Analysis Plot

```{r PCA, fig.align='center', fig.width=9, fig.height=6.5}  
pcaSE(SE_Filt, PlotTitle='First-Second Component', components=c(1,2), Interactive=TRUE, colVec = Cols)
```

```{r PCA_run, fig.align='center', fig.width=9, fig.height=6.5} 
#SE_Filt@colData@listData[["SeqRun"]] <- as.character(SE_Filt@colData@listData[["SeqRun"]])
pcaSE(SE_Filt, PlotTitle='First-Second Component', components=c(1,2), condition = "SeqRun", colVec = seqrun_cols)
```

```{r}
pcaSE_new <- function(SE, PlotTitle = NULL, colVec = NULL, 
                  components = c(1, 2), condition = "Condition", 
                  Interactive = TRUE) 
{
    PCA_list <- calculatePCA(SE, condition = condition)

    if (is.null(PlotTitle)) {
        PlotTitle = deparse(substitute(SE))
    }

    PCData <- PCA_list$PCAData[, c(components, 5, 6)]
    names(PCData) <- c("x_PC", "y_PC", "Sample", "Condition")

    sub <- "Principal Component Analysis"
    pcx <- paste("PC", components[1], "- VarExp: ", round(PCA_list$Var[components[1]], 2))
    pcy <- paste("PC", components[2], "- VarExp: ", round(PCA_list$Var[components[2]], 2))

    if (is.null(colVec)) {
        colVec = (scales::hue_pal())(length(unique(colData(SE)[[condition]])))
    }

    PCAPl <- ggplot(PCData, aes(x = .data$x_PC, y = .data$y_PC)) +
        geom_point(aes(col = .data$Condition), size = 3) +
        labs(x = pcx, y = pcy, title = PlotTitle, subtitle = sub) +
        scale_colour_manual(values = colVec, name = NULL) +
        theme_bw() +
        theme(plot.title = element_text(face = "bold", colour = "darkred", size = 14, hjust = 0.5),
              plot.subtitle = element_text(colour = "darkred", size = 12, hjust = 0.5),
              legend.text = element_text(size = 8),
              legend.position = "bottom")

    if (Interactive == TRUE) {
        PCAPl <- plotly::ggplotly(PCAPl, tooltip = c("Sample", "Condition")) %>%
            plotly::layout(title = list(text = paste0(PlotTitle, "<br>", "<sup>", sub)))
        return(PCAPl)
    } else {
        return(PCAPl) 
    }
}
```

```{r}
ggsave(filename=paste0(OutputFolder, 'PAPER_CORRPLOTS/PCA_run_CTL08.pdf'),
       plot=pcaSE_new(SE_Filt, PlotTitle='First-Second Component', components=c(1,2), condition = "SeqRun", colVec = seqrun_cols, Interactive = FALSE), device='pdf', width=6, height=5)
```


```{r SaveSession}
SessionInfo <- sessionInfo()
Date <- date()
```

```{r SessionInfo}
SessionInfo
Date
``` 
